SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-06-28 scipy-1.0/paper.tex
Formatting adjustments to title in response to reviewer comments in manuscript PR 31.

\title {SciPy - some descriptive title here}

\author[1]{Pauli Virtanen}
\author[2,*]{Ralf Gommers}
\author[3]{TODO}
\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}

@@

% need some better usage stats sources?
% SciPy stuff from njs blog: https://docs.google.com/spreadsheets/d/1lOLvSF0up4eZyv2ugZi-TM_GIs3gPCkGNIDKXS1Y3w4/edit#gid=406031940
From the user side, there have been at least 15 million downloads
of the SciPy manylinux wheels between the start of 2016 and May of 2018
(njs blog). The recommended source for citing SciPy is simply a reference
to the website / library itself\cite{SciPylib}, and has been cited $>3000$
times. Some of the most prominent citing articles include the IPython
publication\cite{PER-GRA:2007}, a heavily-cited Nature Biotechnology
article\cite{pmid17287757}, a dark
matter annihilitation study in the field of
cosmology\cite{1475-7516-2012-08-007}, and many of the
other major downstream software libraries in the Python scientific
computing stack.

>>>>

\title{SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python}

\author[1]{Pauli Virtanen}
\author[2,*]{Ralf Gommers}
\author[3,4]{Tyler Reddy}
\author[5]{Anne Archibald}
\author[6]{Andrew Nelson}
\author[7]{Charles Harris}
\author[8]{CJ Carey}
\author[9]{Denis Laxalde}
\author[10]{Eric Larson}
\author[11]{Eric Moore}
\author[12]{Eric Quintero}
\author[13]{Evgeni Burovski}
\author[14]{Jaime Fernández del Río}
\author[15]{Josef Perktold}
\author[16]{Josh Wilson}
\author[17]{Matthew Brett}
\author[18]{Nikolay Mayorov}
\author[19]{Warren Weckesser}
\author[20]{Matt Haberland}
\author[21]{Scott Sievert}
\author[22]{Yu Feng}
\author[23]{Antonio Horta Ribeiro}

\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[3]{UC Berkeley Institute for Data Science,
          Berkeley, CA, 94720, USA}
\affil[4]{Los Alamos National Laboratory,
	  Theoretical Division 6,
          Los Alamos, NM, 87545, USA}
\affil[5]{Affiliation, department, city, postcode, country}
\affil[6]{Affiliation, department, city, postcode, country}
\affil[7]{Affiliation, department, city, postcode, country}
\affil[8]{Affiliation, department, city, postcode, country}
\affil[9]{Affiliation, department, city, postcode, country}
\affil[10]{Affiliation, department, city, postcode, country}
\affil[11]{Affiliation, department, city, postcode, country}
\affil[12]{Affiliation, department, city, postcode, country}
\affil[13]{Affiliation, department, city, postcode, country}
\affil[14]{Affiliation, department, city, postcode, country}
\affil[15]{Affiliation, department, city, postcode, country}
\affil[16]{Affiliation, department, city, postcode, country}
\affil[17]{Affiliation, department, city, postcode, country}
\affil[18]{Affiliation, department, city, postcode, country}
\affil[19]{Affiliation, department, city, postcode, country}
\affil[20]{Affiliation, department, city, postcode, country}
\affil[21]{Affiliation, department, city, postcode, country}
\affil[22]{Affiliation, department, city, postcode, country}
\affil[23]{Affiliation, department, city, postcode, country}

@@

% need some better usage stats sources?
% SciPy stuff from njs blog: https://docs.google.com/spreadsheets/d/1lOLvSF0up4eZyv2ugZi-TM_GIs3gPCkGNIDKXS1Y3w4/edit#gid=406031940
From the user side, there have been at least 15 million downloads
of the SciPy manylinux wheels between the start of 2016 and May of 2018
(njs blog). The recommended manuscript for citing SciPy,
published online 17 years ago, has been cited $>3000$
times. Some of the most prominent citing articles include the IPython
publication, a heavily-cited Nature Biotechnology article, a dark
matter annihlitation study in the field of cosmology, and many of the
other major downstream software libraries in the Python scientific
computing stack.
